A Proposal for an Intuitionistic Fuzzy Inference System

### 2016-01-08 paper.tex
4/5 Experiments

>>>>

An implementation of the proposed method was developed using the
programming language Clojure, and it is freely accessible at
https://github.com/amherag/intuitionistic-fis. The T1-FISs and
IT2-FISs were developed using Juzzy \cite{wagner2013juzzy}, which
implements T1-FIS, IT2-FIS and GT2-FIS in Java.

The Mackey-Glass time series benchmark was used in order to compare
the performances of each of the FISs, and a Genetic Algorithm (GA) was
used to optimize each of the FISs, so sub-optimal versions of each of
the systems were used for the comparison.

Every FIS uses the following rule base:

where $t_{0}$, $t_{-6}$, $t_{-12}$, and $t_{-18}$ are points in the
Mackey-Glass time series, $t_{0}$ is the present point, $t_{-6}$ is six
points earlier than $t_{0}$, $t_{-12}$ is twelve points earlier, and
$t_{-18}$ is eighteen points earlier. $p_{t+1}$ is the predicted value
for the point $t_{1}$. $A_{1}$, $A_{2}$, $A_{3}$, and $A_{4}$ are
antecedents, and $C_{1}$, $C_{2}$, $C_{3}$, and $C_{4}$ are
consequents.

The search space for the GA consists on eight tuples with the form $\langle
mean, standard deviation \rangle$ for the T1-FIS, $\langle
mean, standard deviation, height \rangle$ for the IFIS, $\langle
mean, standard deviation 1, standard deviation 2 \rangle$ for the
IT2-FIS with uncertain standard deviation, and $\langle
mean 1, mean 2, standard deviation \rangle$ for the IT2-FIS with
uncertain mean, where the means and standard deviations can take
random real numbers from 0 to 100, and the height can take random real
numbers from 0.8 to 1. Each of the individuals in the GA consists on
eight tuples, one for each of the four antecedents and four
consequents in a FIS. The rule base isn't optimized.

Regarding the parameters of the GA, every FIS is optimized for 20
generations, using 100 individuals as the initial population. The
roulette wheel method is used as the selection operator. Five
children are generated each generation and replace the five least
fitted individuals in the population. For the mutation operator, each
individual in the population has a chance of 1\% of suffering an
alteration, which consists on replacing a list of tuples of arbitrary
length from the individual with a
